A new form of transcorrelated Hamiltonian inspired by range-separated DFT

### 2020-12-03 cusp_j/paper/paper.tex
added graphs of TenNo

Coming now to the behaviour of $u(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$. 
\begin{figure*}
 \label{fig_j_mu}
        \includegraphics[width=0.45\linewidth]{small_mu_j.pdf}
        \includegraphics[width=0.45\linewidth]{small_mu_exp_j.pdf}\\
        \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
\end{figure*}
From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.

\subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
\label{sec:ht_general}
\subsubsection{General form of $\tilde{H}[\mu]$ }
Having established the analytical expression of $u(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
\begin{equation}
 \label{ht_def_g}
 e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
\end{equation}
where $\hat{\tau} = \sum_{i<j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
This leads to the following similarity transformed Hamiltonian 
\begin{equation}
 \begin{aligned}
 \label{ht_def_gu}
 \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)  \bigg) \\
           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{u}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{u},\bri{k}),
 \end{aligned}
\end{equation}
where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{u})$ and $\hat{L}(\bri{i},\bri{u},\bri{k})$ are defined as
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1,
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{L}(\bri{1},\bri{2},\bri{3}) ) = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
                                     + & \nabla_3 u(\bri{3},\bri{1}) \cdot \nabla_3 u(\bri{3},\bri{2}).
 \end{aligned}
\end{equation}
Therefore, to obtain the analytical expression of the $\tilde{H}[\mu]$ for a general $N$-electron system, 
one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = u(r_{12},\mu)$.

@@

\section{Application on H$_2$}
Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we study in the last part of the present study study the ground state potential curve of H$_2$ with $ \tilde{H}[\mu]$. 
As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$. 
We report in Figs \ref{}

\begin{figure*}
 \label{fig:mu_1.0_dz_3}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}\\
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_7.pdf}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_9.pdf}\\
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
        \caption{
        H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.  
}
\end{figure*}

@@

According to Eq. \eqref{eq:comtot}, Eq. \eqref{eq:nabla_i_nabla1}, Eq. \eqref{eq:nabla_u2} and Eq. \eqref{eq:lapl_u_final}, the additional terms arising from the commutators in $\tilde{H}[u]$ are (for a two-electron system) 
\begin{equation}
 \begin{aligned}
 \label{eq:comtot2}
 & \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] =  \\
 & -\frac{1}{2} 2 \times \bigg( \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} + \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4}  \bigg) \\
   &- \bigg( 1 - \text{erf}(\mu r_{12})\bigg) \deriv{}{r_{12}}{},
 \end{aligned}
\end{equation}
or equivalently
\begin{equation}
 \begin{aligned}
 \label{eq:comtot2}
 & \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] =  \\
 & -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 - \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
   & + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}.
 \end{aligned}
\end{equation}
Therefore, the full similarity transformed Hamiltonian can be written as
\begin{equation}
  \begin{aligned}
   \tilde{H}[u] = & \sum_{i = 1,2} \bigg( -\frac{1}{2} \big(\nabla_i\big)^2 + v(\br{}_i)  \bigg) + \frac{1}{r_{12}} \\
&   -\frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{}
  \end{aligned}
\end{equation}
or equivalently 
\begin{equation}
  \begin{aligned}
   \tilde{H}[u] = & h_c + \frac{\text{erf}(\mu r_{12})}{r_{12}} + \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} - \frac{\bigg(1 -     \text{erf}(\mu r_{12}) \bigg)^2}{4} \\
& + \bigg( \text{erf}(\mu r_{12}) - 1\bigg) \deriv{}{r_{12}}{},
  \end{aligned}
\end{equation}
which corresponds precisely to Eq. \eqref{eq:h_tilde_r12}.

@@

\subsection{Computation of integrals with $\text{exp}(-\alpha r_{12}^2)$}
As essentially all functions of $r_{12}$ involve directly or indirectly (\textit{i.e.} through a fit) gaussian functions, we will have to evaluate such integrals
\begin{equation}
 \begin{aligned}
  \int \text{d}\br{}_1  \text{d}\br{}_2& \big( x_1 - A_x \big)^{a_x}  \big( x_2 - B_x \big)^{b_x} 
                                         \big( y_1 - A_y \big)^{a_y}  \big( y_2 - B_y \big)^{b_y} 
                                         \big( z_1 - A_z \big)^{a_z}  \big( z_2 - B_z \big)^{b_z} \\
                                       & \text{exp}(-\alpha \big(\br{}_1 - {\bf A} \big)^2)
                                         \text{exp}(-\beta  \big(\br{}_2 - {\bf B} \big)^2)
                                         \text{exp}(-\delta \big(\br{}_1 - \br{}_2 \big)^2)
 \end{aligned}
\end{equation}
which can be transformed into product of types 
\begin{equation}
 \begin{aligned}
  \int \text{d}x_1 \text{d}x_2 & \big( x_1 - A_x \big)^{a_x} \big( x_2 - B_x \big)^{b_x} \\ 
  & \text{exp}(-\alpha \big(x_1 - A_x \big)^2) \text{exp}(-\alpha \big(x_2 - B_x \big)^2) \text{exp}(-\delta \big(x_1 - x_2 \big)^2)
 \end{aligned}
\end{equation}

\section{New form of jastrow factor}
We want the jastrow factor $u(r_{12})$ to fulfil such equation
\begin{equation}
 - \bigg[ \frac{2}{r_{12}} \deriv{u}{r_{12}}{}  + \deriv{u}{r_{12}}{2} \bigg] + \frac{1}{r_{12}} = \frac{\text{erf}\big( \mu r_{12} \big)}{r_{12}}.
\end{equation}
The solution for such an equation is 
\begin{equation}
 u(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2} + \frac{1}{4 r_{12}} \bigg(c_1 - \frac{\text{erf}\big(\mu r_{12} \big)}{\mu^2} \bigg).
\end{equation}
The constant $c_1$ can be found to impose that 
\begin{equation}
 \lim_{r_{12} \rightarrow 0 } u(r_{12}) < \infty,
\end{equation}
which means $c_1 = 0$. Therefore the new jastrow factor is 
\begin{equation}
 u(r_{12}) = \frac{1}{2}r_{12}\bigg( 1 - \text{erf}(\mu r_{12}) \bigg) - \frac{1}{2\sqrt{\pi} \mu} e^{-\big( \mu r_{12}\big)^2}  - \frac{\text{erf}\big(\mu r_{12} \big)}{4 \mu^2 r_{12}}.
\end{equation}

\section{One body term jastrow}
\subsection{The case of the Hydrogen atom}
We want to find a Jastrow factor which will take care of the nuclear-electron cusp condition, and we will begin by the Hydrogen atom.

Let us write the Hamiltonian of the hydrogenoid atom in the radial coordinate for the $l=0$ sector 
\begin{equation}
 H = -\frac{1}{2} \big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{}\big) - \frac{Z}{r}.
\end{equation}
To do so, we have to compute the kinetic part acting on the Jastrow factor acting on a function depending only on the radial coordinate $\phi( r)$
\begin{equation}
 \label{eq:h_atom_j}
 \begin{aligned}
 & -\frac{1}{2}e^{-u(r)}\big(\deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) e^{u(r)}\phi(r)  = \\
 & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) \phi(r) \\
 &-\deriv{u(r)}{r}{}\deriv{}{r}{}\phi(r) \\
 &-\frac{1}{r}\deriv{u(r)}{r}{}\phi(r)  - \frac{1}{2}\deriv{u(r)}{r}{2}\phi(r)  -  \frac{1}{2}\bigg(\deriv{u(r)}{r}{} \bigg)^2 \phi(r).
 \end{aligned}
\end{equation}
Therefore the full similarity transformed Hamiltonian $\tilde{H}[u]$ is 
\begin{equation}
 \begin{aligned}
 \label{eq:one_e_0}
 & e^{-u(r)}H\,e^{u(r)} = \\
 & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) -\deriv{u(r)}{r}{}\deriv{}{r}{}\\
 &-\frac{1}{r}\bigg(\deriv{u(r)}{r}{} + Z \bigg) \\ 
 & - \frac{1}{2}\deriv{u(r)}{r}{2} -  \frac{1}{2}\bigg(\deriv{u(r)}{r}{} \bigg)^2.
 \end{aligned}
\end{equation}
Similarly to what have been proposed in Section \ref{sec:he_j}, we want to find the Jastrow factor $u(r,\mu,Z)$ such that 
\begin{equation}
 \label{eq:one_e_01}
 -\frac{1}{r}\bigg(\deriv{u(r,\mu,Z)}{r}{} + Z \bigg) = -Z\frac{\text{erf}(\mu r)}{r},
\end{equation}
or equivalently
\begin{equation}
 \label{eq:one_e_1}
 \deriv{}{r}{}u(r,\mu,Z) = Z\bigg( \text{erf}(\mu r) - 1\bigg).
\end{equation}
The Jastrow factor fulfilling Eq. \eqref{eq:one_e_1} is 
\begin{equation}
 \label{eq:one_e_2}
 u(r,\mu,Z) = -Z r \bigg( 1 - \text{erf}\big(\mu r\big) \bigg) + \frac{Z}{\sqrt{\pi}\mu} e^{-\big(\mu r \big)^2}. 
\end{equation}
Now, we can plug $u(r,\mu,Z)$ into Eq. \eqref{eq:one_e_0} in order to compute the explicit form of the similarity transformed Hamiltonian. 
To do so, we use Eq. \eqref{eq:one_e_1}, and also that 
\begin{equation}
 \deriv{}{r}{2}u(r) = \frac{2 \mu Z }{\sqrt{\pi}} e^{-(\mu r)^2}.
\end{equation}
One obtains then the similarity transformed Hamiltonian 
\begin{equation}
 \begin{aligned}
 \tilde{H}[u] = & e^{-u(r)} H e^{u(r)} \\
              = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big) - \frac{Z}{r}  \\
                & + Z \bigg( 1 - \text{erf}(\mu r)\bigg) \deriv{}{r}{} \\
                & - Z \frac{\text{erf}(\mu r) - 1}{r} \\
                & -Z \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} \\
                & - \frac{1}{2}Z^2 \bigg( \text{erf}(\mu r) -1 \bigg)^2,
 \end{aligned}
\end{equation}
and one can notice that the $\frac{-Z}{r}$ interaction cancels out to give
\begin{equation}
 \label{eq:one_e_3}
 \begin{aligned}
 \tilde{H}[u] = & e^{-u(r)} H e^{u(r)} \\
              = & -\frac{1}{2}\big( \deriv{}{r}{2} + \frac{2}{r} \deriv{}{r}{} \big)  \\
                & -Z \bigg[ \frac{\mu}{\sqrt{\pi}} e^{-(\mu r)^2} + \frac{\text{erf}(\mu r)}{r} + \frac{1}{2}Z \bigg( \text{erf}(\mu r) -1 \bigg)^2 \bigg] \\
                & + Z \bigg( 1 - \text{erf}(\mu r)\bigg) \deriv{}{r}{}. 
 \end{aligned}
\end{equation}
Therefore, compared to the usual Hamiltonian, the similarity transformed Hamiltonian contains a different local interaction which is clearly non divergent, but also a new short-range differential operator.

\subsection{General equation}
Now that we know the general form of the one-body Jastrow factor for a one electron system, we can generalize it 
to an $N$-electron system and an $M$ nucleus system by just taking the following form 
 e^{\hat{\tau}({\bf r}_1,\hdots , {\bf r}_i,{\bf r}_N)} = e^{-\sum_i^N u({\bf r}_i)} 
where $u({\bf r}_i)$ has the following form 
 u({\bf r}_i) = \sum_{A} u(r_{iA},\mu,Z_A) 
where $u(r,\mu,Z)$ is given by Eq. \eqref{eq:one_e_2} and $r_{iA} = \big|{\bf r}_i - {\bf R}_A \big|$. 
According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the equation of the similarity transformed Hamiltonian is similar  
to that of Eq. \eqref{ht_def_g} but with a new form of Jastrow factor. 
Therefore one needs to compute $\big[ H,\hat{\tau} \big]$ and $\frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]$. 
Let us begin by $\big[ H,\hat{\tau} \big]$, and as before, we apply it to a general function $\phi(\br{}_1,\hdots \br{}_N)$:
 \label{eq:one_com1_1}
 \bigg[ H, \hat{\tau} \bigg]\phi(\br{}_1,\hdots \br{}_N) & = \bigg[ -\frac{1}{2} \sum_i \nabla^2_i, \sum_{u} u(\br{}_j) \bigg]      \phi(\br{}_1,\hdots \br{}_N) \\    
                                                        & = -\frac{1}{2} \sum_i \bigg( \big(\nabla^2_i u({\bf r}_i)\big) + 2\nabla_i u({\bf r}_i) \cdot \nabla_i \phi(\br{}_1,\hdots \br{}_N) \bigg).  
Therefore, one can write that term as
 \label{eq:one_com1_2}
  \big[ H,\hat{\tau} \big] =& -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg) \\
                            & -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg).
After some math, the second-order commutator is simply 
 \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = -\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
So eventually, the similarity transformed operator becomes 
& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg)    
                                                                   -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
                                                                   -\frac{1}{2}\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
Therefore, the addition of the jastrow operator does not add extra two-body terms. 
\subsection{Computation of the total operator}
\subsubsection{Computation of $\nabla_i u(\br{}_i)$}
&\nabla_i u(\br{}_i) = \sum_A \nabla_i u(r_{iA},Z_A) \\
                    &= \sum_A \deriv{}{x_i}{} u(r_{iA},Z_A) {\bf e}_{x_i} + \deriv{}{y_i}{} u(r_{iA},Z_A) {\bf e}_{y_i} + \deriv{}{z_i}{} u(r_{iA},Z_A) {\bf e}_{z_i}, 
 \deriv{}{x_i}{}u(r_{iA}) = \deriv{}{r_{iA}}{}u(r_{iA}) \deriv{r_{iA}}{x_i}{},
and as $r_{iA} = \sqrt{(x_1 - x_A)^2 + (y_1 - y_A)^2 + (z_1 - z_A)^2} $ 
 \deriv{r_{iA}}{x_1}{} = \frac{x_1 - x_A}{r_{iA}}
and therefore according to Eq. \eqref{eq:one_e_1}, one has 
 \deriv{}{x_i}{} u(r_{iA},Z_A) = -\sum_A Z_A \big( x_i - x_A \big) \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}.
\subsubsection{Computation of $\nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i)$}
The computation of $\nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i)$ leads to 
  \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) =  \sum_{A,B} Z_B &Z_A \big( x_i - x_A \big) \big( x_i - x_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\
                                                                      & +  \big( y_i - y_A \big) \big( y_i - y_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}} \\ 
                                                                      & +  \big( z_i - z_A \big) \big( z_i - z_B \big)  \frac{ 1 -\text{erf}(\mu r_{iA})}{r_{iA}} \frac{ 1 - \text{erf}(\mu r_{iB})}{r_{iB}}.
The diagonal part of such integrals is simply
 &  \sum_{A} (Z_A)^2 \bigg(\big( x_i - x_A \big)^2 +  \big( y_i - y_A \big)^2 + \big( z_i - z_A \big)^2\bigg) \frac{\bigg(\text{erf}(\mu r_{iA}) - 1\bigg)^2}{\big(r_{iA}\big)^2}\\ 
  = & \sum_{A} (Z_A)^2 \bigg( \text{erf}(\mu r_{iA}) -1 \bigg)^2

\subsubsection{Computation of $\nabla^2_i u(\br{}_i) $}
We need to compute 
 \deriv{}{x_{i}}{2} u(\br{}_i) & = -\sum_A Z_A \deriv{}{x_i}{} \bigg[(x_i - x_A) \frac{1 - \text{erf}(\mu r)}{r_{iA}} \bigg] \\
                               & = -\sum_A Z_A \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
But, one has that
 \deriv{}{x_i}{} \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} = - \frac{(x_i - x_A)}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg).
Therefore, 
 \label{eq:lapl_important}
 (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} = - \frac{(x_i - x_A)^2}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg)
\end{equation}.
Therefore, the Laplacian is 
 \label{eq:lapl_interm_1}
&  \deriv{}{x_{i}}{2} u(\br{}_i) + \deriv{}{y_{i}}{2} u(\br{}_i) + \deriv{}{z_{i}}{2} u(\br{}_i) =  - \sum_{A} Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \\
 & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  \bigg]
But according to Eq. \eqref{eq:lapl_important}, one has that 
 & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  = \\
 &- \frac{(x_i - x_A)^2 + (y_i - y_A)^2 + (z_i - z_A)^2}{(r_{iA})^2} \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg)
which is simply 
 \label{eq:lapl_interm_2}
 & + (x_i - x_A) \deriv{}{x_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (y_i - y_A) \deriv{}{y_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \\ 
 & + (z_i - z_A) \deriv{}{z_i}{}\frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  = \\
 &- \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg).
Then, coming back to Eq. \eqref{eq:lapl_interm_1} with Eq. \eqref{eq:lapl_interm_2} one has 
 \Delta_i u(\br{}_i) = - \sum_{A}  Z_A \bigg[ 3 \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \bigg( \frac{2 \mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2} + \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}\bigg) \bigg]
which becomes 
 \Delta_i u(\br{}_i) = - \sum_{A}  2 \, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg]
\subsubsection{Computation of the total operator}
& H + \big[ H,\hat{\tau} \big] + \frac{1}{2} \bigg[ \big[H,\hat{\tau}\big],J\bigg] = \\ & H -\frac{1}{2} \bigg( \sum_i \nabla^2_i u(\br{}_i) \bigg)    
                                                                   -\sum_i \bigg(\nabla_i u(\br{}_i) \bigg) \cdot \bigg( \nabla_i  \bigg)  
                                                                   -\frac{1}{2}\sum_i \nabla_i u({\bf r}_i) \cdot \nabla_i u({\bf r}_i) 
which becomes
  \tilde{H} = H +&  \sum_i \sum_{A}\, Z_A  \bigg[ \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}}  - \frac{\mu}{\sqrt{\pi}} e^{-(\mu r_{iA})^2}  \bigg] \\
           &+  \frac{1 - \text{erf}(\mu r_{iA})}{r_{iA}} \bigg[ (x_i - x_A) \deriv{}{x_i}{} + (y_i - y_A) \deriv{}{y_i}{} + (z_i - z_A) \deriv{}{z_i}{}\bigg] \\
           - \frac{1}{2}\sum_{B} Z_B &\bigg[ \big( x_1 - x_A \big) \big( x_1 - x_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\
           &+  \big( y_1 - y_A \big) \big( y_1 - y_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB}} \\ 
           &+  \big( z_1 - z_A \big) \big( z_1 - z_B \big)  \frac{\text{erf}(\mu r_{iA}) - 1}{r_{iA}} \frac{\text{erf}(\mu r_{iB}) - 1}{r_{iB} } \bigg].
and as $H = \sum_i -\frac{1}{2} \Delta_i - \sum_A \frac{Z_A}{r_{iA}} + \sum_{i>j} \frac{1}{r_{ij}} $ the total interaction becomes 

>>>>

Coming now to the behaviour of $u(r_{12};\mu)$as a function of the parameter $\mu$, we report in Figure \ref{fig_j_mu} its dependence on $r_{12}$ for a set of values of $\mu$, together with that of $\mathcal{J}(r_{12};\mu)$. 
\begin{figure*}
 \label{fig_j_mu}
        \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_j.pdf}
        \includegraphics[width=0.45\linewidth]{plots/jastrow/small_mu_exp_j.pdf}\\
        \caption{Shape of $u(r_{12};\mu)$ (up) and of $\mathcal{J}(r_{12};\mu) = \text{exp}\bigg(u(r_{12};\mu) \bigg) $ (bottom) for different values of $\mu$.}
\end{figure*}
From Figure\ref{fig_j_mu}, one can see that: i) the larger the $\mu$, the more short-range is $u(r_{12};\mu)$, ii) the larger the $\mu$, the closer $u(r_{12};\mu)$ is from 0 and therefore the less impact the correlating factor has on the wave function, iii) the smaller the $\mu$, the deeper is the hole imposed by $\mathcal{J}(r_{12};\mu)$.

\subsection{The general analytical form of  $\tilde{H}[\mu]$ and some of its properties}
\label{sec:ht_general}
\subsubsection{General form of $\tilde{H}[\mu]$ }
Having established the analytical expression of $u(r_{12};\mu)$, one can derive the general expression of the associated transcorrelated Hamiltonian.  
According to Eq. (2) of Ref. \onlinecite{CohLuoGutDobTewAla-JCP-19}, the similarity transformed Hamiltonian can be written as 
\begin{equation}
 \label{ht_def_g}
 e^{-\hat{\tau}} \hat{H} e^{\hat{\tau}} = H + \big[ H,\hat{\tau} \big] + \frac{1}{2}\bigg[ \big[H,\hat{\tau}\big],\hat{\tau}\bigg]
\end{equation}
where $\hat{\tau} = \sum_{i<j}u(\br{}_i,\br{}_j)$ and $\hat{H} = \sum_i -\frac{1}{2} \nabla^2_i + v(\br{}_i) + \sum_{i<j} \frac{1}{r_{ij}}$. 
This leads to the following similarity transformed Hamiltonian 
\begin{equation}
 \begin{aligned}
 \label{ht_def_gu}
 \tilde{H} & = H - \sum_i \bigg( \frac{1}{2} \nabla_i^2 \hat{\tau} + \big(\nabla_i \hat{\tau} \big) + \frac{1}{2} \big(\nabla_i \hat{\tau} \big)^2  \bigg) \\
           & = H - \sum_{i<j} \hat{K}(\bri{i},\bri{u}) - \sum_{i<j<k} \hat{L}(\bri{i},\bri{u},\bri{k}),
 \end{aligned}
\end{equation}
where the effective two- and three-body operators $\hat{K}(\bri{i},\bri{u})$ and $\hat{L}(\bri{i},\bri{u},\bri{k})$ are defined as
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{K}(\bri{1},\bri{2}) ) = \frac{1}{2} \bigg( &\nabla_1^2 u(\bri{1},\bri{2}) + \nabla_2^2u(\bri{1},\bri{2}) \\
                                               + &\big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 + \big(\nabla_1 u(\bri{1},\bri{2}) \big) ^2 \bigg) \\
                                               + &\nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_2 + \nabla_2 u(\bri{1},\bri{2}) \cdot \nabla_1,
 \end{aligned}
\end{equation}
\begin{equation}
 \begin{aligned}
 \label{def_k}
  \hat{L}(\bri{1},\bri{2},\bri{3}) ) = & \nabla_1 u(\bri{1},\bri{2}) \cdot \nabla_1 u(\bri{1},\bri{3}) + \nabla_2 u(\bri{2},\bri{1}) \cdot \nabla_2 u(\bri{2},\bri{3})  \\
                                     + & \nabla_3 u(\bri{3},\bri{1}) \cdot \nabla_3 u(\bri{3},\bri{2}).
 \end{aligned}
\end{equation}
Therefore, to obtain the analytical expression of the $\tilde{H}[\mu]$ for a general $N$-electron system, 
one needs to compute the actual form of the operators $\hat{K}(\bri{1},\bri{2})$ and $\hat{L}(\bri{1},\bri{2},\bri{3})$ when $u(\bri{1},\bri{2}) = u(r_{12},\mu)$.

@@

\section{Application on H$_2$}
Having established in Sec \ref{sec:ht_general} the analytical form of $ \tilde{H}[\mu]$ for a general molecular system, we study in the last part of the present study study the ground state potential curve of H$_2$ with $ \tilde{H}[\mu]$. 
As in the study of the helium atom of Sec \ref{sec:total_h}, in a given basis set $\basis$ and for a given geometry, we use RHF molecular orbitals and the full flexibility is given to the eigenvectors $\ket{\phimub}$. 
We report in Figs \ref{fig:H2} the difference with respect to the estimated exact ground state potential energy curve using several levels of calculations.

\begin{figure*}
 \label{fig:H2}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_3.pdf}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_5.pdf}\\
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_7.pdf}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_mu_0_9.pdf}\\
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_lda.pdf}
        \includegraphics[width=0.45\linewidth]{plots/H2/H2_de_fci_rsc.pdf}\\
        \caption{
        H$_2$ molecule: Error with respect to the estimated exact ground state energy for the aug-cc-pVDZ and aug-cc-pVTZ basis sets (AVDZ, AVTZ, respectively) as a function of the inter nuclear distance for different values of $\mu$, and comparison with FCI.  
}
\end{figure*}

@@

@@

\bibliography{srDFT_SC}
